SPARQL on the Open, Decentralised Web

### 2016-08-03 dissertation/related.tex
Improve desc of Hartig, #21

Olaf Hartig has a large number of papers that are adjacent to the
present work, including his Ph.D. dissertation \cite{hartig2014querying} where he
explores querying Linked Data, i.e. query data that is not contained
in an \textit{a priori} defined collection of RDF data, but where resources
are traversed to compute a result. Hartig provides solid formal
foundations for such query processing, as well as computational
feasibility, soundness and completeness. The most relevant paper to
this work is \cite{hartig2011caching}.

>>>>

Olaf Hartig has a large number of papers that are adjacent to the
present work, including his Ph.D. dissertation \cite{hartig2014querying} where he
explores querying Linked Data, i.e. query data that is not contained
in an \textit{a priori} defined collection of RDF data, but where resources
are traversed to compute a result. Hartig provides solid formal
foundations for such query processing, as well as computational
feasibility, soundness and completeness. The most relevant paper to
this work is \cite{hartig2011caching}. In that work, he considers the
impact of caching on performance and completeness. Completeness is
important in the context of query answering when the collection is not
defined, and the cache may therefore provide results that were not
accessible for some reason, at query time. Hartig finds many cases
where it is profitable to cache, but also cases where it is not.
